---
title: "Lab 00 - Hello IDS!"
author: "Kiet Lam"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Edwin", "Jack", "Ruth", 
           "Sid", "Mingxi"),
  github_username = c("Edw12", "JackHutcheson", "RuthAsh", 
                      "siddhantpujni", "Jiang-Mingxi"), 
  colour = c("red", "green", "purple", 
             "purple", "red"),
  hobby = c("cooking", "football", "Watching movies", 
            "basketball", "reading"),
  favourite_number = c(5, 4, 2, 7, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The graph above shows the favourite number of each github user, with the colour of their bar being their favourite colour. 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github username", 
          y = "Favourite number",
          title = "Github user and their favourite number")
```



### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Any other data visualisation that is suitable for discrete values, rather than this bar chart as you cannot have a decimal value when it comes to the count of people.

